\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{fancyhdr}
\pagestyle{fancy}

\title{SE 3XA3: Problem Statement\\Ultimate Tic Tac Toe }

\author{Team 3, Tic Tac Toe
		\\ Kunal Shah | shahk24
		\\ Pareek Ravi | ravip2
}

\date{September 23 2016}

\input{../Comments}

\begin{document}
\lhead{Team 3 - Problem Statement}
\rhead{Ultimate Tic Tac Toe}
\maketitle

\noindent \textbf{What problem are you trying to solve?}

We are trying to solve the problem of boredom. Tic Tac Toe is a classic game 
everyone has played multiple times. It is hard to make a match last for more 
than a few minutes. The original game is very simple with minimal strategy and 
complexity. Tic Tac Toe is often played on paper but unfortunately the modern 
day not many people carry around a pen and pad of paper. These are all 
problems that limit the ability to play the original game Tic Tac Toe.\\

\noindent \textbf {Why is this an important problem?}

This is an important problem because it provides people with an solution to 
play a game similar to the original game Tic-Tac-Toe which just as easy to 
play. Ultimate Tic-Tac-Toe is beneficial because it offers a more challenging 
game dynamic. If young kids were to play this rather than regular Tic-Tac-Toe, 
it would allow them think more strategically. People often would rather opt to 
not play a game rather than try to play a game with complex rules such as 
chess, but a game Ultimate Tic Tac Toe would be just as stimulating to the 
brain, but at the same time has very simple rules that people would enjoy to 
play.\\

\noindent \textbf {What is the context of the problem you are solving?}

This game will attract users of all ages on all platforms, as our version of 
Tic Tac Toe will be easy to play and accessible. The target environment is for 
people to be playing this game whenever they have a few minutes to spare. 
Instead of simply wasting time, people can engage each other in a strategic 
game. As long as people have a stable internet connection and a little free 
time, they can enjoy this game online regardless of platform, Windows, MacOS, 
Mobile, Desktop etc. This also allows users to enjoy the game without 
downloading it, but at the same time, will have real time updates to make the 
game play smoothly.\\

\newpage

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
September 23 & Kunal Shah & Initial setup\\
September 23 & Kunal Shah & Problem Statement \\
... & ... & ...\\
\bottomrule
\end{tabularx}
\end{table}

\end{document}